Atmospheric escape and star-planet-interaction in the HAT-P-67 b system

### 2022-11-21 paper/paper1/ms.tex
Add an observation log to the paper, may add/remove columns later...
Some text about the HPF observations

The Habitable Zone Planet Finder Spectrograph \citep[HPF][]{2012SPIE.8446E..1SM,2014SPIE.9147E..1GM, 2019Optic...6..233M} on the queue-scheduled 10-meter \emph{Hobby-Eberly Telescope} \citep[HET][]{1998SPIE.3352...34R} operates in the near-IR from $8100-12800~\AA\;$ spanning the \textit{z}, \textit{Y}, and \textit{J} bands. We observed HAT-P-67 with HPF on a total of 26 unique nights.  The HET fixed-elevation design \citep{2007PASP..119..556S} limits the observability of HAT-P-67 to about 1 hour ``tracks'', compared to conventional steerable telescopes that can conduct point-and-stare observations for hours.  We organized the observations into four campaigns to coincide with HAT-P-67b transits on 2020 April 28, 2020 May 22, 2020 June 15, and 2022 April 28.  These in-transit nights had 12-18 exposures per HET track, with integration times between 5-8.5 minutes.  These campaigns were designed to acquire out-of-transit observations one and two nights before and after transit, weather and schedule permitting.  These out-of-transit observations typically received 4 or fewer individual exposures.  Additionally we acquired random-in-phase observations using low priority ``P4'' time.

Finally, the observation scheduling was strategically restricted to the spring season when the Barycentric Earth Radial Velocity (BERV) would Doppler shift telluric absorption lines sufficiently far away from the core of the Helium 10833$\AA~$ feature.  The small BERV still means the redward Helium linewing has significant telluric contamination between 10834-10836$\AA$, but the core and blue line wings appear pristine.

\input{tables/observations_flat_table.tex}

>>>>

The Habitable Zone Planet Finder Spectrograph \citep[HPF][]{2012SPIE.8446E..1SM,2014SPIE.9147E..1GM, 2019Optic...6..233M} on the queue-scheduled 10-meter \emph{Hobby-Eberly Telescope} \citep[HET][]{1998SPIE.3352...34R} operates in the near-IR from $8100-12800~\AA\;$ spanning the \textit{z}, \textit{Y}, and \textit{J} bands. We observed HAT-P-67 with HPF on a total of 39 unique nights.  The HET fixed-elevation design \citep{2007PASP..119..556S} limits the observability of HAT-P-67 to less than 1 hour ``tracks'' for a fixed range of hour angles before and after the meridian; whereas conventional steerable telescopes can conduct point-and-stare observations for hours, HET cannot.  We organized the observations into four campaigns to coincide with HAT-P-67b transits on 2020 April 28, 2020 May 22, 2020 June 15, and 2022 April 28.  These in-transit nights had up to exposures per HET track, with integration times between 5-8.5 minutes.  Table \ref{tabHPFLog} summarizes the log of observations.  These campaigns were designed to acquire out-of-transit observations one and two nights before and after transit, weather and schedule permitting.  These out-of-transit observations typically received 4 or fewer individual exposures.  Additionally we acquired random-in-phase observations using low priority ``P4'' time.

The observation scheduling was strategically restricted to the spring season when the Barycentric Earth Radial Velocity (BERV) would Doppler shift telluric absorption lines sufficiently far away from the core of the Helium 10833$\AA~$ feature.  The small BERV still means the redward Helium linewing has significant telluric contamination between 10834-10836$\AA$, but the core and blue line wings appear pristine.

Only 19 out of the 39 nights possess A0V telluric calibration standard stars.  These standard stars, when available, we used to spot-check our masking procedure.

\begin{deluxetable*}{lrrrccr}
    \tablewidth{0pc}
    \tabletypesize{\scriptsize}
    \tablecaption{
        HPF Observation Log
        \label{tabHPFLog}
    }
    \tablehead{
        \colhead{Date}   &
        \colhead{Track} &
        \colhead{Transit?} &
        \colhead{BTJD} &
        \colhead{$N_\mathrm{exp}$} &
        \colhead{$t_\mathrm{exp}$} &
        \colhead{$\phi$}\\
        \colhead{}   &
        \colhead{} &
        \colhead{} &
        \colhead{(days)} &
        \colhead{} &
        \colhead{(s)} &
        \colhead{$\in(-0.5, 0.5)$}
    }
    \startdata
    \input{tables/observation_log.tex}
    \enddata
\end{deluxetable*}
